---
output:
  md_document:
    variant: gfm
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Lifecycle:Experimental](https://img.shields.io/badge/Lifecycle-Experimental-339999)](https://github.com/bcgov/repomountie/blob/master/doc/lifecycle-badges.md)
[![License](https://img.shields.io/badge/License-Apache%202.0-blue.svg)](https://opensource.org/licenses/Apache-2.0)

```{r, echo=FALSE, results='asis', message=FALSE}
library("envreportutils")
```


# # biodiversity-detailed-assessment

### Data

The analysis uses data from several sources. Certain datasets need to be manually downloaded prior to starting processing. Information about where datasets can be found is in `dataset-info.txt`. 
    
### Targets Workflow

This project leverages the `targets` package, a pipeline toolkit for data science projects in R. You can install `targets` from CRAN:

```{r}
#install.packages("targets")
```
#Usage
Run `targets::tar_make()` to run project. This will run all of the analysis - no individual scripts are required. 

### Required R packages

The packages used in this analysis are catalogued in `packages.R`. The packages will be loaded automatically with `tar_make()` but some may need to be installed prior to initiating the workflow. 


